From centralized certification systems to more internet-like ones

### 2015-12-25 paper.tex
title Sovereign keys
Orthograph
Working on sovereign keys

% Define document title and author
	\title{From a centralized certification systems to a more internet-like one}
	\author{Alexandre Kervadec
	\thanks{Tutor : A.Guermouche}}
	\markboth{University of Bordeaux -- Master 2 Computing Sciences - Networking and mobile systems}{}
	\maketitle

@@

@@

@@

@@

>>>>

% Define document title and author
	\title{From centralized certification systems to more internet-like ones}
	\author{Alexandre Kervadec
	\thanks{Tutor : A.Guermouche}}
	\markboth{University of Bordeaux -- Master 2 Computing Sciences - Networking and mobile systems}{}
	\maketitle

@@

\begin{figure}[!hbt]
	\begin{center}
	\includegraphics[width=\columnwidth]{pki.png}
	\label{fig:pki}
	\caption{Diagram of the X.509 and CAs process (from \cite{wang2015domain})}
	\end{center}
\end{figure}

@@

\begin{figure}[!hbt]
	\begin{center}
	\includegraphics[width=\columnwidth]{danereq.png}
	\label{fig:pki}
	\caption{Process of certificate verification (from \cite{wang2015domain})}
	\end{center}
\end{figure}

@@

\subsection{Sovereign keys}
\label{sovkeys}

Sovereign keys are an Electric Frontier Foundation (EFF) proposition.

A sovereign key is a cryptographic pair of key where the public key is associated to a domain name (or a subdomain) to create a trust anchor\footnote{A trust anchor is an authoritative entity for which trust is assumed and not derived \cite{wallace2010}.} for itself.\\
This association \textit{public key/domain name} is registered in a append-only data structure, kept on servers named ''\textit{timeline servers}''. There is a small number, around 10-20, of these \cite{eck2014}.\\
The private part of the sovereign key (private key) allows to sign certificates of which the CN is the domain (or subdomain) name which it is associate with.\\
During a handshake with a TLS server, the certificate is sent with its protected domain key signature, by the same mecanism than a TLS transaction based on PKIX. The client has then the possibility to recover the public key associated with that sovereign key from the timeline servers to check the key validity, that the domain is the same that the one in the current transaction and that it signs the receive certificate.

@@

\bibitem{wallace2010} Wallace, C. Trust Anchor Format. No. RFC 5914. 2010.

\bibitem{eck2014} P. Eckersley, ''Sovereign key cryptography for internet domains'', online, 2012, https://git.eff.org/?p=sovereign-keys.git;a=blob\_plain;f=sovereign-key-design.txt;hb=master, last retrieved on December 21, 2014.

\bibitem{wang2015domain} Wang, Xinli, Yan Bai, and Lihui Hu. "Domain based certification and revocation." Proceedings of the 2015 International Conference on Security and Management, SAM. Vol. 15. 2015.
